Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-01-28 Ben_Manuscripts/Paper1/Paper1_Outline.tex
editing outline

	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
	%Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item Small number of layers create micellar structure %MRS3: specify.
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}
%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
	FIGURE: initial configuration \\
	caption: A representative initial configuration \\
	\\
	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
	\begin{itemize}
		\item SAXS gives an idea of Pore-to-Pore distances
		\item TEM images and rejection give a pore size estimate
		\item Ran long NPT simulations at 300 K and 1 bar ( $>$200 ns )
	\end{itemize}

@@

	Proper selection of initial structural parameters results in an equilibrated model that is experimentally consistent 
	\begin{itemize}
		\item Visual perspective \\
%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
		FIGURE: show top view and cross section (with pbcs on)\\
		caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
		(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
		\item System validated using multiple monomer configurations 
                  %MRS3: be mroe precise what ``validation'' means.
		\item Pore to pore distance
		\begin{itemize}
			\item We know from SAXS data what the distance between pores should be
			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
			\item Simulated SAXS data
		\end{itemize}
                %MRS3: see above on putting in thesis and what you are trying to convince readers.
		FIGURE - perhaps a four panel figure
		(a) Experimental Small Angle X-ray scattering data \\
		(b) Equilibration of pores monitored by measuring the distance between pores over time \\
		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\  	
		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
	\end{itemize}

>>>>

	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
	%Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
	\begin{itemize}
		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
		\item 5 layers create micellar structure %MRS3: specify.
		\item Beyond 20 layers is unnecessary to get expected configuration
		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
	\end{itemize}
%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
%BJC3: Maybe i include this in the supplemental information. I don't think a picture of the initial configuration is actually that interesting or important 
	FIGURE: initial configuration \\
	caption: A representative initial configuration \\
	\\
	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
	\begin{itemize}
		\item SAXS gives an idea of Pore-to-Pore distances
		\item TEM images and rejection give a pore size estimate
		\item Ran long NPT simulations at 300 K and 1 bar ( $>$200 ns )
	\end{itemize}

@@

	Proper selection of initial structural parameters results in an equilibrated model that is experimentally consistent 
	\begin{itemize}
		\item Visual perspective \\
%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
		FIGURE: shows top view and cross section (with pbcs on)\\
		%caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
		%(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
			caption: % BJC3: Attempt #2 trying to make it more thesis like. These aren't meant to do much other than show that we get, qualitatively, the same strucure described in the literature
		(a) The expected hexagonal membrane morphology is preserved upon equilibration
		(b) Straight cylindrical pore regions are present 
		\item System validated using multiple monomer configurations 
                  %MRS3: be mroe precise what ``validation'' means.
		\item Pore to pore distance
		\begin{itemize}
			\item We know from SAXS data what the distance between pores should be
			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
			\item Simulated SAXS data
		\end{itemize}
                %MRS3: see above on putting in thesis and what you are trying to convince readers.
		FIGURE - perhaps a four panel figure
		(a) Experimental Small Angle X-ray scattering data \\
		(b) Equilibration of pores monitored by measuring the distance between pores over time \\
		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\  	
		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
	\end{itemize}
